Supplementary Figures relative to feature selection

### 2020-05-13 main_figures/dimensionality.Rmd
fixed label colors in heatmaps

```{r figure6, fig.width=9, fig.height=9.5}
pdf("dimensionality.pdf", width=9, height=10)
plot_grid( p1, p2, p3, nrow=3, labels=c(NA,LETTERS[3:4]))
dev.off()
plot_grid( p1, p2, p3, nrow=3, labels=c(NA,LETTERS[3:4]))
```

>>>>

```{r figure6, fig.width=9, fig.height=9.5}
pdf("dimensionality.pdf", width=9, height=10.5)
plot_grid( p1, p2, p3, nrow=3, labels=c(NA,LETTERS[3:4]))
dev.off()
plot_grid( p1, p2, p3, nrow=3, labels=c(NA,LETTERS[3:4]))
```

### 2020-05-13 main_figures/normalization.Rmd
fixed label colors in heatmaps

p1 <- renameNorm(evalHeatmap(res, step="dimreduction", what="log10_total_counts", scale=FALSE, show_heatmap_legend = TRUE, name="adj.R2", what2="PC1.covar.adjR2", agg.by = "norm", reorder_rows = TRUE, col=viridisLite::viridis(100), row_split = classifyNorms(norm), row_title="Variance in PC1 explained by covariate") + 
  evalHeatmap(res, step="dimreduction", what="log10_total_features", scale=FALSE, show_heatmap_legend = FALSE, what2="PC1.covar.adjR2", agg.by = "norm", reorder_rows = TRUE, col=viridisLite::viridis(100)))

>>>>

p1 <- renameNorm(evalHeatmap(res, step="dimreduction", what="log10_total_counts", scale=FALSE, show_heatmap_legend = TRUE, name="adj.R2", what2="PC1.covar.adjR2", agg.by = "norm", reorder_rows = TRUE, col=viridisLite::viridis(100), row_split = classifyNorms(norm), row_title="Variance in PC1 explained by covariate", value_cols=c("black","black")) + 
  evalHeatmap(res, step="dimreduction", what="log10_total_features", scale=FALSE, show_heatmap_legend = FALSE, what2="PC1.covar.adjR2", agg.by = "norm", reorder_rows = TRUE, col=viridisLite::viridis(100), value_cols=c("black","black")))

### 2020-05-13 main_figures/svadea.Rmd
fixed label colors in heatmaps

hts <- evalHeatmap( res, step="dea", what="logFC.pearson", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85, scale="colCenterScale" ) +
  evalHeatmap( res, step="dea", what="TPR", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85, scale="colCenterScale", filterExpr=threshold==0.05 ) +
  evalHeatmap(res, step="dea", what="FDR", agg.by=c("sva.method","k"), row_split="sva.method", 
                     anno_legend=FALSE, show_column_names=TRUE, font_factor=0.85, scale="colCenterScale",
                     col=rev(viridisLite::inferno(100)), value_cols=c("white","black"), filterExpr=threshold==0.05)
hts <- pipeComp:::.renameHrows(hts, f = function(x) gsub("none > 1", "none",x, fixed=TRUE))
#draw(hts, heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=.scaledLegend())

>>>>

hts <- evalHeatmap( res, step="dea", what="logFC.pearson", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85 ) +
  evalHeatmap( res, step="dea", what="TPR", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85, filterExpr=threshold==0.05 ) +
  evalHeatmap(res, step="dea", what="FDR", agg.by=c("sva.method","k"), row_split="sva.method", 
                     anno_legend=FALSE, show_column_names=TRUE, font_factor=0.85, 
                     col=rev(viridisLite::inferno(101)), value_cols=c("white","black"), filterExpr=threshold==0.05)
hts <- .renameHrows(hts, f = function(x) gsub("none > 1", "none",x, fixed=TRUE))
#draw(hts, heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=.scaledLegend())

### 2020-05-13 supplementary_figures/supp_overall.Rmd
fixed label colors in heatmaps

**A:** Proportion of the variance in clustering accuracy metrics explained by main parameters. **B:** Proportion of the variance in Adjusted Rand Index (ARI) explained by the parameters, among the analyses giving the true number of clusters. In both panels, the proportion is calculated after accounting for differences due to the dataset, the resolution and their interaction.

>>>>

**A:** Proportion of the variance in clustering accuracy metrics explained by main parameters. **B:** Proportion of the variance in Adjusted Rand Index (ARI) explained by the parameters, among the analyses giving the true number of clusters. The ANOVA were performed with the model

`metric ~ dataset*resolution+doubletmethod+filt+norm+clustmethod+dims`

In both panels, the proportion is calculated after substracting the variance attributable to differences due to the dataset, the resolution and their interaction. The alternatives included in the analysis (other than the default ones described in the methods) were: 
```
list( doubletmethod=c("none","doublet.scDblFinder"),
      filt=c("none","filt.default","filt.stringent"),
      norm=c("norm.seurat","norm.sctransform","norm.scran"),
      sel=c("sel.vst","sel.deviance","sel.expr"),
      selnb=c(2000,4000),
      dr=c("seurat.pca"),
      dims=c("elbow", 10, "maxLikGlobal"),
      clustmethod=c("clust.seurat","clust.scran.knnAnnoy") )
```
